Continuous time

### 2023-09-25 continuous-time.qmd
more sensitivity analyses

>>>>

### Functional form of `hours` and `pre`
Here we'll investigate the impact of the assumed functional form of `hours` and `pre`. As can be seen in @fig-lmm-pre-interaction-sens-pre, that impact of the assumed functional form of `pre` has very little impact on the results.

```{r}
#| label: fig-lmm-pre-interaction-sens-pre
#| fig-cap: Estimated trends for various functional forms of `pre`
tmp_models <- list()
tmp_models[["linear"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-pre-linear.Rds",
  lmer(
    mood100 ~ ns4(hours) * pre + (1 + ns4(hours) | pid) + (1 | ps),
    data = dat_pre
  )
)
tmp_models[["ns2"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-pre-ns2.Rds",
    lmer(
      mood100 ~ ns4(hours) * ns(pre, 2) + (1 + ns4(hours) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models[["ns3"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-pre-ns3.Rds",
    lmer(
      mood100 ~ ns4(hours) * ns(pre, 3) + (1 + ns4(hours) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models[["ns4"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-pre-ns4.Rds",
    lmer(
      mood100 ~ ns4(hours) * ns(pre, 4) + (1 + ns4(hours) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models[["ns5"]] <- fit3

get_trend_by_model <- function(fit, model_label) {
  emm <- emmeans(
    fit,
    ~ hours + pre,
    at = list(
      hours = seq(0, 3, length.out = 100),
      pre = pre_values
    ),
    lmer.df = "asymp"
  )
  as.data.frame(emm) |>
    mutate(
      pre = factor(
        round(pre),
        labels = pre_labels,
      ),
      model = model_label
    )
}
tmp_p <- map2(
  tmp_models,
  names(tmp_models),
  \(fit, lab) get_trend_by_model(fit, lab)
) |>
  bind_rows()
p_pre_x_sens <- tmp_p |>
  ggplot(
    aes(
      hours,
      emmean,
      group = interaction(model, pre),
      color = model,
      linetype = pre
    )
  ) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL,
      fill = model,
      color = NULL
    ),
    alpha = 0.10,
    show.legend = FALSE
  ) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  scale_x_hours
p_pre_x_sens
```

Next, we'll lok at `hours`. In @fig-lmm-pre-interaction-sens-hours we see that the results aren't fundamentally different using splines with less degrees of freedom, or even a linear term.

```{r}
#| label: fig-lmm-pre-interaction-sens-hours
#| fig-cap: Estimated trends for various functional forms of `hours`  
tmp_models2 <- list()
tmp_models2[["linear"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-hours-linear.Rds",
  lmer(
    mood100 ~ hours * ns(pre, 5) + (1 + hours | pid) + (1 | ps),
    data = dat_pre
  )
)
tmp_models2[["ns2"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-hours-ns2.Rds",
    lmer(
      mood100 ~ ns(hours, 2) * ns(pre, 5) + (1 + ns(hours, 2) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models2[["ns3"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-hours-n3.Rds",
  lmer(
    mood100 ~ ns(hours, 3) * ns(pre, 5) + (1 + ns(hours, 3) | pid) + (1 | ps),
    data = dat_pre,
  )
)
tmp_models2[["poly2"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-hours-poly2.Rds",
  lmer(
    mood100 ~ poly(hours, 2) * ns(pre, 5) + (1 + poly(hours, 2) | pid) + (1 | ps),
    data = dat_pre,
  )
)
tmp_models2[["ns4"]] <- fit3
tmp_p <- map2(
  tmp_models2,
  names(tmp_models2),
  \(fit, lab) get_trend_by_model(fit, lab)
) |>
  bind_rows()
p_pre_x_sens %+% tmp_p 
```
